Topics Causal Inference

### 2024-08-16 documents/paper.tex
Add table and figure notes.

\documentclass[11pt, a4paper, leqno]{article}
\usepackage{a4wide}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{float, afterpage, rotating, graphicx}
\usepackage{epstopdf}
\usepackage{longtable, booktabs, tabularx}
\usepackage{fancyvrb, moreverb, relsize}
\usepackage{eurosym, calc}
% \usepackage{chngcntr}
\usepackage{amsmath, amssymb, amsfonts, amsthm, bm}
\usepackage{caption}
\usepackage{mdwlist}
\usepackage{xfrac}
\usepackage{setspace}
\usepackage[dvipsnames]{xcolor}
\usepackage{subcaption}
\usepackage{minibox}
% \usepackage{pdf14} % Enable for Manuscriptcentral -- can't handle pdf 1.5
% \usepackage{endfloat} % Enable to move tables / figures to the end. Useful for some
% submissions.
\DeclareMathOperator{\E}{E}
\usepackage{multirow}

@@

\section{Simulation Results}
Throughout the simulations I use $N=10,000$ observations and $40$ simulation repetitions, corresponding to \cite{wager2018estimation}.
This low number is chosen to make the problem computationally feasible.
I use $100$ trees in all causal forest estimators and a sub-sampling share of $0.2$.
These parameters are much smaller than in the original~\cite{wager2018estimation} to reduce the run-time of the simulation.
I still find very similar results in the replication parts, as outlined below.
I follow~\cite{wager2018estimation} and report the expected MSE and expected coverage for CATE estimation by evaluating the predictions of the estimator on a new sample, also of size $10,000$.
To give an indication of noisiness coming from both a low number of simulations and approximating expected MSE and coverage, I also report the standard deviation of simulation runs.
For generic machine learning simulations I use a standard random forest as the baseline learner for $b_0(Z) = \E[Y(0)|Z]$ and a causal forest with similar hyperparameters as above for estimating $s_0(Z)$.

@@

\begin{table}
    \caption{Simulation Results: WA Replication and WGAN}
    \center
    \begin{tabular}{lccccccc}
        & Dimension & MSE (True) & SD & MSE (Pop) & SD & Coverage & SD \\
        \toprule
        \multicolumn{8}{l}{\textit{Panel A:\ Original WA DGP 3}} \\
        \input{../bld/wa_replication/tables/wa_replication_dgp3.tex} \\
        \midrule

@@

        \multicolumn{8}{l}{\textit{Panel D:\ Placebo}} \\
        \input{../bld/wa_replication/tables/wa_replication_dgp6.tex} \\
        \bottomrule
    \end{tabular}

@@

\begin{table}
    \caption{Simulation Results: ML Generic --- Cate Estimation}
    \center
    \begin{tabular}{lcc}
        Dimension & MSE & SD \\
        \toprule
        \multicolumn{3}{l}{\textit{Panel A:\ Original WA DGP 3}} \\
        \input{../bld/generic_ml/tables/generic_ml_dgp3.tex} \\
        \midrule

@@

        \multicolumn{3}{l}{\textit{Panel D:\ Placebo}} \\
        \input{../bld/generic_ml/tables/generic_ml_dgp6.tex} \\
        \bottomrule
    \end{tabular}

@@

% Generic ML: BLP and GATES Coverage
\begin{table}
    \caption{Simulation Results: ML Generic --- BLP and GATES Coverage}
    \center
    \begin{tabular}{lccccccc}
        Dimension & \multicolumn{7}{c}{Coverage} \\
        \toprule
        \multicolumn{8}{l}{\textit{Panel A:\ Original WA DGP 3}} \\
        \input{../bld/generic_ml/tables/generic_ml_blp_gates_coverage_dgp3.tex} \\
        \midrule

@@

@@

@@

>>>>

\documentclass[11pt, a4paper, leqno]{article}
\usepackage{a4wide}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
% \usepackage{float} % Note: incompatible with floatrow
\usepackage{afterpage, rotating, graphicx}
\usepackage{epstopdf}
\usepackage{longtable, booktabs, tabularx}
\usepackage{fancyvrb, moreverb, relsize}
\usepackage{eurosym, calc}
% \usepackage{chngcntr}
\usepackage{amsmath, amssymb, amsfonts, amsthm, bm}
\usepackage{caption}
\usepackage{mdwlist}
\usepackage{xfrac}
\usepackage{setspace}
\usepackage[dvipsnames]{xcolor}
\usepackage{subcaption}
\usepackage{minibox}
% \usepackage{pdf14} % Enable for Manuscriptcentral -- can't handle pdf 1.5
% \usepackage{endfloat} % Enable to move tables / figures to the end. Useful for some
% submissions.
\DeclareMathOperator{\E}{E}
\usepackage{multirow}
\usepackage{threeparttable}
\usepackage[capposition=top]{floatrow}

@@

\section{Simulation Results}
Throughout the simulations I use $N=10,000$ observations and $40$ simulation repetitions, corresponding to \cite{wager2018estimation}.
This low number is chosen to make the problem computationally feasible.
I use $100$ trees in all causal forest estimators and a sub-sampling share of $0.2$.
These parameters are much smaller than in the original~\cite{wager2018estimation} to reduce the run-time of the simulation.
I still find very similar results in the replication parts, as outlined below.
I follow~\cite{wager2018estimation} and report the expected MSE and expected coverage for CATE estimation by evaluating the predictions of the estimator on a new sample, also of size $10,000$.
To give an indication of noisiness coming from both a low number of simulations and approximating expected MSE and coverage, I also report the standard deviation of simulation runs.
For generic machine learning simulations I use a standard random forest as the baseline learner for $b_0(Z) = \E[Y(0)|Z]$ and a causal forest with similar hyperparameters as above for estimating $s_0(Z)$.
When analysing group average treatment effects (GATES), I define five groups based on the treatment effect quintiles predicted by the ML proxy.
To approximate the true GATES induced by the proxy I estimate this on a large sample of size $N=1,000,000$; as noted in the paper, if the size of the auxiliary sample diverges the randomness due to splitting and training the proxy can be ignored.
I use a main, auxiliary splitshare of $0.5$ throughout the analysis.

@@

\begin{table}
    \caption{Simulation Results: WA Replication and WGAN}
    \begin{threeparttable}
        \center
        \begin{tabular}{lccccccc}
            & Dimension & MSE (True) & SD & MSE (Pop) & SD & Coverage & SD \\
            \toprule
            \multicolumn{8}{l}{\textit{Panel A:\ Original WA DGP 3}} \\
            \input{../bld/wa_replication/tables/wa_replication_dgp3.tex} \\
            \midrule

@@

            \multicolumn{8}{l}{\textit{Panel D:\ Placebo}} \\
            \input{../bld/wa_replication/tables/wa_replication_dgp6.tex} \\
            \bottomrule
        \end{tabular}
        \begin{tablenotes}
            \small
            \item \textbf{Notes}: This table reports simulation results for~\cite{wager2018estimation}.
            Results for $40$ simulation runs with number of observations $N=10,000$, number of trees $200$ and resampling share $0.2$.
            \textit{Dimension} refers to the number of covariates in the DGP\@. \textit{Standard} DGP refers to sampling directly from the DGP, while \textit{WGAN} DGP refers to sampling from a WGAN trained based on a sample from the given DGP.
            MSE and coverage are calculated based on a test sample of $10,000$ observations. MSE \textit{TRUE} evaluates against the true CATE function of the respective DGP, while MSE \textit{Pop} evaluates against a CATE function estimated based on a (large) population draw and only applies to the WGAN DGP.
            Panel A reports results for the third DGP in~\cite{wager2018estimation}; Panel B and C increase the heterogeneity of the CATE function to 4 and 8 covariates, respectively; Panel D reports results for a CATE of zero (placebo).
            For details see the text.
        \end{tablenotes}
    \end{threeparttable}
\end{table}

@@

\begin{table}
    \caption{Simulation Results: ML Generic --- Cate Estimation}
    \begin{threeparttable}
    \center
    \begin{tabular}{lcc}
        Dimension & MSE & SD \\
        \toprule
        \multicolumn{3}{l}{\textit{Panel A:\ Original WA DGP 3}} \\
        \input{../bld/generic_ml/tables/generic_ml_dgp3.tex} \\
        \midrule

@@

        \multicolumn{3}{l}{\textit{Panel D:\ Placebo}} \\
        \input{../bld/generic_ml/tables/generic_ml_dgp6.tex} \\
        \bottomrule
    \end{tabular}
    \begin{tablenotes}
        \small
        \item \textbf{Notes}: This table reports simulation results for~\cite{chernozhukov2023genml}.
        In the auxiliary sample the BCA is estimated by a random forest regressor, while the CATE is estimated by a causal forest.
        Results for $40$ simulation runs with number of observations $N=10,000$, number of trees $200$ and resampling share $0.2$.
        \textit{Dimension} refers to the number of covariates in the DGP\@.
        MSE and coverage are calculated based on a test sample of $10,000$ observations. SD refers to the standard deviation of this quantity over the simulation runs.
        Panel A reports results for the third DGP in~\cite{wager2018estimation}; Panel B and C increase the heterogeneity of the CATE function to 4 and 8 covariates, respectively; Panel D reports results for a CATE of zero (placebo).
        For details see the text.
    \end{tablenotes}
\end{threeparttable}

@@

% Generic ML: BLP and GATES Coverage
\begin{table}
    \caption{Simulation Results: ML Generic --- BLP and GATES Coverage}
    \begin{threeparttable}
        \center
        \begin{tabular}{lccccccc}
            Dimension & \multicolumn{7}{c}{Coverage} \\
            & \multicolumn{2}{c}{Best Linear Predictor} & \multicolumn{5}{c}{Group Average Treatment Effects} \\
            & $\beta_1$ & $\beta_2$ & $\gamma_1$ & $\gamma_2$ & $\gamma_3$ & $\gamma_4$ & $\gamma_5$ \\
            \toprule
            \multicolumn{8}{l}{\textit{Panel A:\ Original WA DGP 3}} \\
            \input{../bld/generic_ml/tables/generic_ml_blp_gates_coverage_dgp3.tex} \\
            \midrule

@@

        \begin{tablenotes}
            \small
            \item \textbf{Notes}: This table reports simulation results for~\cite{chernozhukov2023genml} studying coverage for the BLP and GATES parameters (five groups).
            In the auxiliary sample the BCA is estimated by a random forest regressor, while the CATE is estimated by a causal forest.
            Results for $40$ simulation runs with number of observations $N=10,000$, number of trees $200$ and resampling share $0.2$.
            \textit{Dimension} refers to the number of covariates in the DGP\@.
            MSE and coverage are calculated based on a test sample of $10,000$ observations. SD refers to the standard deviation of this quantity over the simulation runs.
            Panel A reports results for the third DGP in~\cite{wager2018estimation}; Panel B and C increase the heterogeneity of the CATE function to 4 and 8 covariates, respectively; Panel D reports results for a CATE of zero (placebo).
            For details see the text.
        \end{tablenotes}
    \end{threeparttable}
\end{table}

@@

     \floatfoot{\textbf{Notes}: This figure reports simulation results for GATES parameters of the generic machine learning approach.
     For each of the four DGPs, it plots the distribution of each of the five GATE parameter estimates over the simulation runs.
     The dashed line indicates the true GATES using a large population draw. Sample size $N=10,000$ and $40$ simulation runs.
     }

@@

     \floatfoot{\textbf{Notes}: This figure reports simulation results for CLAN of the generic machine learning approach.
     For each of the four DGPs, it plots the distribution of the estimated characteristics for the first four covariates over the simulation runs.
     The dashed line indicates the true characteristics of the least and most affected group estimated from a large sample.
     Sample size $N=10,000$ and $40$ simulation runs.
     }
